Mining the human microbiome for clinical insight

### 2018-11-27 chap5.tex
Brainstorm content for limitations + extensions

\section{Summary and limitations of reported work}

@@

>>>>

\section{Summary}

@@

\section{Limitations of reported work}

Associations not causation: in all three projects, I only show associations. Need to go back and validate with larger patient cohorts and orthogonal confirmations (mechanistic model organism studies, randomized trials, culturing bugs to check that they matter, etc)

Taxonomy but not function-based: in all three projects, I mostly focus on what we can learn from 16S data. But function is probably way more relevant: need to look at metagenomics or transcriptomics. And also, strains are really the thing that matters in this data. For FMT stuff especially, will need robust ways to track strains in complex communities.

Sample sizes: even though aerodigestive in the largest cohort, it's still too small to make robust inferences about things of interest (like reflux). Even though 30 datasets is a lot, it's nowhere near the size of "real" meta-analyses. And, as we show in donor selection chapter, sample size will continue to be a limitation in trying to extract new discoveries from FMT trials.

\section{Perspective and extensions}

\subsection{Re-analyzing existing datasets is awesome}

Allows for people to come and ask new questions easily.

Second and third projects: what can we learn from existing data?

In combining existing data, challenge is batch effects (but we sort of developed a method to address this)

Also

In the future, all data should be publicly available so people can ask interesting new questions and have data readily available to test their hypotheses.

\subsection{Partnerships between clinicians and bioinformaticians are crucial}

First project literally couldn't be done without Rachel.

Second project: included datasets from clinical studies and research studies, made the paper much stronger! (Also much harder, lulz)

Third project: illustrates the power of putting the two expertises together

\subsection{Extracting knowledge from information should always be the goal}

First project: have to go beyond just looking for statistical significance and try to figure out what would be clinically meaningful.

Second project: just listing bugs doesn't mean anything if you don't contextualize them

Third project: need to incorporate your a priori knowledge into everything you do. Have to think about *why* a trial would fail, and whether or not you think that's legit or not. Also, remember to try very hard to ask better questions at the outset of a clinical trial.
